Robust Estimation, Prediction and Control with \\ Linear Dynamics and Generic Costs

### 2020-02-10 main.tex
Updates from Overleaf

\begin{figure}[t]
	\centering
	\includegraphics[trim={0 2cm 0 0}, clip, width=0.6\linewidth]{img/ellipsoid}
	\caption{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}. The size of the confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
	\label{fig:estimation}
\end{figure}

@@

In both experiments, we used $\gamma=0.9$ and $\delta=0.9$.
The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are gaussian with covariance $\Sigma_r = 0.1 I_s$.

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[trim={0 2cm 0 0}, clip, width=0.6\linewidth]{img/ellipsoid}
	\caption{The model estimation procedure, running on the obstacle avoidance problem of \autoref{sec:experiments}. The confidence region $C_{[N],\delta}$ shrinks with the number of samples $N$.}
	\label{fig:estimation}
\end{figure}

@@

In both experiments, we used $\gamma=0.9$,  $\delta=0.9$ and a planning budget $K=100$. The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are gaussian with covariance $\Sigma_r = 0.1 I_s$.
